\blue Thesis - draft \\ \blueb NB-IoT

### 2022-05-03 writing/draft.tex
Progress

\newcommand{\tilv}[1]{\textbf{\color{ymagreen} [#1]}}
\newcommand{\note}[1]{\textbf{\color{ymagray}[#1]}}
\newcommand{\highlight}[1]{{\bluen{#1}}}
\newcommand{\hghlght}[1]{\textbf{\color{ymaorng} #1}}
\newcommand{\point}[1]{\textbf{\color{ymared} #1}}
\newcommand{\rem}[1]{{\red{\textbf{REMOVE:}} \red{\sout{#1}}}}

@@

% -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
% Kafli
% -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
\clearpage
\section{NB-IoT}

@@

\hghlght{It is important to describe the physical channels, since the analysis goes on about identifying when they reach congestion}. \point{Needs to be investigated if the higher layer channels introduce any limitation.}

@@

The access process is as follows: \hghlght{These steps have to be verified from \cite{3gpp}}
\begin{enumerate}
  \item Random access: the device initiates a connection with the base station using the random channel
  \begin{enumerate}
    \item Here the possibility of collision with other devices occurs i.e. when two devices try to access at same time they interfere and neither of them gets through
    \item \hghlght{What is the retry mechanism ?}
  \end{enumerate}
  \item The base station assigns resources on the dedicated channels \point{freeing resources from the random access channel ??}
  \item When the device has gotten its dedicated resources it can begin transmitting
\end{enumerate}

The capacity limit is reached when the number of devices increases, partly due to the probability of collisions and partly due to the capacity of the dedicated channels. \hghlght{The point of the paper is to identify which one is congested before.}

\point{Notes:}\vspace{-4mm}
\begin{itemize}
  \item \hghlght{Investigate how the paging mechanism is implemented in NB-IoT. There must be some way for the base station to reach the UE.}
\end{itemize}

@@

When the user has gotten the random access procedure completed and is scheduled on the transmission channels. The next step is the focus of the thesis - how to maximise ??, to be able to service more users and withholding the goal of minimum transmission.w

@@

@@

@@

\hghlght{Statement:} For a device with 164 dB coupling loss, a 10-year battery life can be reached if the UE transmits 200-byte data a day on average {[TR 45.820 v13.1.0, “Cellular system support for ultra low complexity and low throughput internet of things,” Nov. 2015]}

>>>>

\newcommand{\tilv}[1]{\textbf{\color{ymagreen}[#1]}}
\newcommand{\note}[1]{\textbf{[\color{ymablue}#1}]}
\newcommand{\highlight}[1]{{\bluen{#1}}}
\newcommand{\hh}[1]{\textbf{\color{ymaorng} #1}}
\newcommand{\point}[1]{\textbf{\color{ymared} #1}}
\newcommand{\rem}[1]{{\red{\textbf{REMOVE:}} \red{\sout{#1}}}}

@@

% -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
% Kafli
% -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
\clearpage
\section{NB-IoT}\label{theo}

@@

\hh{It is important to describe the physical channels, since the analysis goes on about identifying when they reach congestion}. \point{Needs to be investigated if the higher layer channels introduce any limitation.}

@@

The access process is as follows: \hh{These steps have to be verified from \cite{3gpp}}
\begin{enumerate}
  \item Random access: the device initiates a connection with the base station using the random channel
  \begin{enumerate}
    \item Here the possibility of collision with other devices occurs i.e. when two devices try to access at same time they interfere and neither of them gets through
    \item \hh{What is the retry mechanism ?}
  \end{enumerate}
  \item The base station assigns resources on the dedicated channels \point{freeing resources from the random access channel ??}
  \item When the device has gotten its dedicated resources it can begin transmitting
\end{enumerate}

The capacity limit is reached when the number of devices increases, partly due to the probability of collisions and partly due to the capacity of the dedicated channels. \hh{The point of the paper is to identify which one is congested before.}

\point{Notes:}\vspace{-4mm}
\begin{itemize}
  \item \hh{Investigate how the paging mechanism is implemented in NB-IoT. There must be some way for the base station to reach the UE.}
\end{itemize}

@@

When the user has gotten the random access procedure completed and is scheduled on the transmission channels. The next step is the focus of the thesis - how to maximise ??, to be able to service more users and withholding the goal of minimum transmission.

@@

% -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
% HERMUN
% -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
\clearpage
\section{Simulation}

To simulate the environment there are a number of key features that need to be taken into account:

\begin{itemize}
\item What is the expected number of UE trying to send \note{base this on articles}
\item How frequent do the UE send like eg. how many times a day \note{base this on articles}
\item What is the package size that is sent per transmission (full session) \note{base this on articles}
\item And how long does it take to process the package
\end{itemize}

The simulation is a Python script relying on the package SimPy. This is an event driven simulation package, but currently the events aren't used. Instead it is utilised such that one step represents one TTI. The script could be extended to have a limited number of RACH channels \note{assuming it is one available per TTI}, thus making use of the built in features as events.

\subsection{Assumptions}

The initial assumption, is to look at an area of one base station (eNodeB). According to Ericsson blog \cite{lme_web1} the base station can serve an area up to 40 km and have around 50.000 connections on the cell. A more pragmatic solution is to look at a rural area of 20 km radius. Such an area can have \hh{xx} homes. If a home is expected to have \hh{yy} NB-IoT devices, the scenario gives \hh{xx*yy} connections.

Here the focus is on smart metering devices. A measurement is sent every 5-15 minuttes and the size of the package is \hh{bb}. \note{The package size is random variable with \?\? distribution}

@@

\bibitem{lme_web1}
Ericsson. (2019).
\textit{What is NB-IoT? Practical tips to unlock its business potential}.
Ericsson blog.
\url{https://www.ericsson.com/en/blog/2019/10/what-is-nb-iot}

@@

\hh{Statement:} For a device with 164 dB coupling loss, a 10-year battery life can be reached if the UE transmits 200-byte data a day on average {[TR 45.820 v13.1.0, “Cellular system support for ultra low complexity and low throughput internet of things,” Nov. 2015]}
